SST_patterns

### 2020-04-06 SST_patterns.Rmd
update

ggplot(data =final_intensity, aes(x = intensity_mean)) +
  geom_histogram(aes(fill = product),  
                       position = "dodge", alpha=0.6) +
  # labs(x = "Duration (Days)", y = "Number of upwelling signals", colour = "Temperature products") +
  facet_wrap(~site) +
theme_bw() ---
title: "SST_patterns"
author: "Amieroh Abrahams"
date: "19 August 2019"
output: html_document
---
# This script is for all the various datasets

@@

@@

@@

## Comparing the relationship between 10 km and 30km from coastline and 10km and 50km from the coastline

combined <- rbind(CMC_count,G1SST_count,MUR_count,OISST_count)
```

>>>>

ggplot(data =final_intensity, aes(x = intensity_mean)) +
  geom_histogram(aes(fill = product),  
                       position = "dodge", alpha=0.6) +
  # labs(x = "Duration (Days)", y = "Number of upwelling signals", colour = "Temperature products") +
  facet_wrap(~site) +
theme_bw() ---
title: "SST_patterns"
author: "Amieroh Abrahams"
date: "19 August 2019"
output: html_document

knitr::opts_chunk$set(
  comment = "R>",
  warning = FALSE,
  message = FALSE 
)
#update.packages() 
library(tidyverse)
library(lubridate)
library(ggpubr)
library(zoo)
library(FNN)
library(scales)
library(gridExtra)
library(circular)
library(fossil)
library(mapproj)
library(broom)
# library(ncdf4) # This was used to process NetCDF files in an earlier version
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(fasttime)
library(xtable)
library(ncdf4) # library for processing netCDFs
library(data.table)
# library(plyr) # RWS: Never load the plyr package as it interferes with the tidyverse
library(heatwaveR)
library(grid)
library(ggthemes)
```

@@

metric_func <- function(df){
 metrics <-df %>% 
  filter(year(date_start) %in% 2011:2014) %>% 
  #mutate(year = year(date_start)) %>% 
  group_by(distance, site) %>% 
  summarise(mean_intensity = mean(intensity_mean),
            sum_events = sum(event_no)) %>% 
   select(site, distance, mean_intensity, sum_events)
}

@@

# No of upwelling events found at the different sites
SACTN_metrics <- SACTN_upwell_base %>% 
  filter(year(date_start) %in% 2011:2014) %>% 
  group_by(site) %>% 
  summarise(mean_intensity = mean(intensity_mean),
            sum_events = sum(event_no)) %>% 
  select(site, mean_intensity, sum_events)

@@

## Using series of general linear hypothese to look for differences in upwelling signal metrics between datasets and between sites
# Is there a significant difference in the duration/intensity etc between the datasets at a particular site

```{r}
load("Data/OISST_final.RData")
load("Data/G1SST_final.RData")
load("Data/SACTN_upwell_base.RData")
load("Data/MUR_final.RData")
load("Data/CMC_final.RData")

combined_products <- rbind(OISST_final,CMC_final,SACTN_upwell_base,MUR_final,G1SST_final)

metric_4years <- combined_products %>% 
   filter(year(date_start) %in% 2011:2014)
